Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2017-03-02 manuscript/editor_response2_tree_physiology.Rmd
maunscript comment edits

\
- *Comment: 2. Increasing rather than decreasing C sink activity is another approach that you did not mentioned in your introduction.*
I was done on rubber tree by comparing trees that are tapped for latex production with trees that are not tapped. You may have a look on the two following papers and see whether or not it can be included in your introduction.
Silpi, U., Lacointe, A., Kasempsap, P., Thanysawanyangkura, S., Chantuma, P., Gohet, E., Musigamart, N., Clément, A., Améglio, T., Thaler, P., 2007. Carbohydrate reserves as a competing sink: evidence from tapping rubber trees. Tree Physiology 27, 881–889.

Kanpanon, N., Kasemsap, P., Thaler, P., Kositsup, B., Gay, F., Lacote, R., Epron, D., 2015. Carbon isotope composition of latex does not reflect temporal variations of photosynthetic carbon isotope discrimination in rubber trees (Hevea brasiliensis). Tree Physiology 35, 1166–1175.

@@

@@

@@

@@

\
*Response*: Reworded the desciprtion of the findings with the g~1~ parameter. "The *g*~1~ parameter ... was highest in the smaller containers and decreased in larger containers and the Free seedling treatment"

>>>>

\
- *Comment: 2. Increasing rather than decreasing C sink activity is another approach that you did not mentioned in your introduction. It was done on rubber tree by comparing trees that are tapped for latex production with trees that are not tapped. You may have a look on the two following papers and see whether or not it can be included in your introduction.*

\
*Response*: Although both studies with rubber trees are extremely interesting in terms of the dymanics of storage carbohyrdate accumluation and mobilization, they lack empirical data for photosynthesis rates and only speculate about the impacts on growth. I have choosen to not mention them in the introduction, as they are mostly out of context with discusssion of the effects of sink limitation on physiological processes and growth.

@@

\
*Response*: We have corrected to this statement to include observed values of *g*~s~, *A*~sat (which includes C~a~ of 400) and vapor presssure deficit.

@@

\
*Response*: Reference to Atkin has been removed.

@@

\
*Response*: We have now introducted the term *A*~mass~ in this section as it had not been previously described.

@@

\
*Response*: We have reworded the desciprtion of the findings with the g~1~ parameter. "The *g*~1~ parameter ... was highest in the smaller containers and decreased in larger containers and the Free seedling treatment"

### 2017-03-02 manuscript/manuscript_pve_editor.Rmd
maunscript comment edits

\
*P*~day~  was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *g*~1~ and *R*~dark~) for each treatment and meteorological data from an onsite weather station. Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above). The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values. *R*~dark~ was was estimated using Eq. (2) from @atkin2005response, which was parameterized with a mean reference empirical measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.

\
(2)
$$R~dark~ = R_{ref}Q_{10}~^{(T-T_{ref})/10}$$
Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked]. Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, net leaf photosynthesis rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment. *P*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h. This resulted in 120 unique values of *P*~day~  for each soil volume treatment, one value for each day of the experiment. Thus, each daily time step for model runs included a value of *P*~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.

@@

##Data analysis
Differences in measured parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels. Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different. A linear mixed effect model of *A*~mass~ and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R. Explained variance (*R*^2^) of mixed models were computed as in @nakagawa2013general, in which the marginal *R*^2^ represents variance explained by fixed factors and the conditional *R*^2^ by both fixed and random factors. Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr]. All tests of statistical significance were conducted at an $\alpha$ level of 0.05.

>>>>

\
*P*~day~  was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *g*~1~ and *R*~dark~) for each treatment and meteorological data from an onsite weather station. Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above). The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed values of *g*~s~, *A*~sat~ and vapour pressure deficit. *R*~dark~ was was estimated using Eq. (2), which was parameterized with a mean reference empirical measurement for each treatment, a Q~10~ value of 1.86, a reference air temperature for each treatment and air temperatures at each time step.

\
(2)
$$R~dark~ = R_{ref}Q_{10}~^{(T-T_{ref})/10}$$
Methods of the coupled leaf gas exchange model are also described in Duursma et al. [-@duursma2014peaked]. Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, net leaf photosynthesis rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment. *P*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h. This resulted in 120 unique values of *P*~day~  for each soil volume treatment, one value for each day of the experiment. Thus, each daily time step for model runs included a value of *P*~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.

@@

##Data analysis
Differences in measured parameters with soil volume were analysed by mixed-effects models in R with individual containers and experimental blocks as random effects and soil volume treatment as a categorical fixed effect with seven levels. Tukey's post-hoc tests were performed in conjunction with ANOVA to determine which specific paired comparisons among soil volume treatments were different. A linear mixed effect model of *A*~max~ on a mass basis (*A*~mass~) and leaf chemistry was performed using the 'nlme' package [@Pinheiro2015] in R. Explained variance (*R*^2^) of mixed models were computed as in @nakagawa2013general, in which the marginal *R*^2^ represents variance explained by fixed factors and the conditional *R*^2^ by both fixed and random factors. Tests of allometric relationships between log-transformed biomass components were implemented using standardized major axis regression in the 'smatr' package in R [@warton2012smatr]. All tests of statistical significance were conducted at an $\alpha$ level of 0.05.
